The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
update lcres and nobs results

<!-- TODO: make sure we clarify these are means of all individuals? -->
<!-- TODO: discuss layer similarity for social threshold -->

@@

Increasing landcover resolution resulted in a decreased proportion of forage, a
rare and patchy habitat, and corresponding low connectivity of individuals in
these habitats. Mean graph strength increased consistently in winter forest and
open habitats. Mean graph strength in winter forage <!-- TODO: check this fig
A/C similar lines--> Individuals in summer layers had consistent weak
connections. Layer relevance was stable in winter for open and forest habitats
but decreased for forage habitats (Figure \@ref(fig:lcres)b). Layer relevance
was stable for all habitat classes in summer layers. Layer similarity was stable
for forest and open, except for a sharp decrease in layer similarity in open at
100 m and 250 m<!-- TODO: check this fig A/C similar lines--> (Figure
\@ref(fig:lcres)c). Layer similarity was not possible to calculate between
winter and summer forage because, at all landcover resolutions greater than 30
m, there were no individuals connected in the network layers. Individuals still
used forage habitats but given a lower availability due to increasing landcover
resolution, at a much lower rate. Connective redundancy slightly decreased as
landcover resolution increased (Figure \@ref(fig:lcres)d). These results
indicate the importance of matching landcover resolution to scale of selection
as well as ensuring the landcover product used has a resolution fine enough to
detect landscape features and habitats relevant to study species.

As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics appeared to stabilize. Mean graph
strength varied in winter layers becoming stable at ~200 m and remained
consistently weak in summer layers (Figure \@ref(fig:nobs)a). Layer relevance in
winter layers increased between ~10 m and ~50 m observations, remaining stable
with additional observations (Figure \@ref(fig:nobs)b). <!-- TODO: update with
fix for open/rerun --> Like coarse landcover resolution (Figure
\@ref(fig:lcres)), low numbers of observations were not sufficient for capturing
individuals in all contexts and therefore layer similarity could not be
calculated below approximately <!--TODO: update these -->75 observations for
forest, approximately 210 observations for open and approximately 300
observations for forage (Figure \@ref(fig:nobs)c). Once sufficient observations
were obtained, layer similarity stabilized for all three landcover classes at
approximately 200 observations for forest and approximately 300 observations for
open and forage landcover types. Connective redundancy increased dramatically
between ~10 m and ~50 m observations before stabilizing with all new
observations included (Figure \@ref(fig:nobs)d). Given the observed trend of
these multilayer metrics stabilizing after a certain number of observations are
included, the results suggest this sensitivity method could be useful for
determining the number of observations necessary for sufficiently describing
social dynamics across contexts.

>>>>

@@

Increasing landcover resolution resulted in a decreased proportion of forage, a
rare and patchy habitat, and corresponding low connectivity of individuals in
these habitats. Mean graph strength increased consistently in winter forest and
open habitats. Mean graph strength in winter forage varied across landcover
resolutions with an increase at 250 m and decrease at 500 m. Individuals in
summer layers had consistent weak connections. Layer relevance was stable in
winter for open and forest habitats but decreased for forage habitats (Figure
\@ref(fig:lcres)b). Layer relevance was stable for all habitat classes in summer
layers. Layer similarity was stable for forest and open, except for a sharp
decrease in layer similarity in open at 100 m and 250 m (Figure
\@ref(fig:lcres)c). Layer similarity was not possible to calculate between
winter and summer forage because, at all landcover resolutions greater than 30
m, there were no individuals connected in the network layers. Individuals still
used forage habitats but given a lower availability due to increasing landcover
resolution, at a much lower rate. Connective redundancy slightly decreased as
landcover resolution increased (Figure \@ref(fig:lcres)d). These results
indicate the importance of matching landcover resolution to scale of selection
as well as ensuring the landcover product used has a resolution fine enough to
detect landscape features and habitats relevant to study species.

As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics appeared to stabilize. Mean graph
strength varied in winter layers at low number of observations, becoming stable
at ~75 observations and was consistently weak in summer layers (Figure
\@ref(fig:nobs)a). Layer relevance in winter layers increased between ~10 m and
~100 m observations, remaining stable with additional observations (Figure
\@ref(fig:nobs)b). Like coarse landcover resolution (Figure \@ref(fig:lcres)),
low numbers of observations were not sufficient for capturing individuals in all
contexts and therefore layer similarity could not be calculated below ~30
observations for forest, approximately ~80 observations for open (Figure
\@ref(fig:nobs)c). Layer similarity was not possible to calculate for forage
layers because there were no connected individuals in summer forage. Once
sufficient observations were obtained, layer similarity was relatively stable
for forest and open layers. Connective redundancy increased dramatically between
~10 m and ~50 m observations before stabilizing with all new observations
included (Figure \@ref(fig:nobs)d). Given the observed trend of these multilayer
metrics stabilizing after a certain number of observations are included, the
results suggest this sensitivity method could be useful for determining the
number of observations necessary for sufficiently describing social dynamics
across contexts.
